---
title:  <h3>Microsoft Machine Learning Stack for BI & Analytics</h3>
author: <h5>Andreas Effraimis<h5>
output: 
  revealjs::revealjs_presentation:
    theme: night
    center: false
---

# BI tools and ML integration

## Power BI & R integration

We can integrate Power BI with R either to visualize analytical outcomes or self contain an ML model within our dashboards

There are two ways of doing this :

- Create an R data source 
- Create an R visual and execute an external R script

## Power BI ML models

R scripting essentially gives the Power BI user the ability to integrate ane ML models within business dashboads and answer not only descriptive questions but also prescriptive and predictive.

- Traditional BI [ What happend? ]
- Data Science  [ Why it happend? What will happen? ]

# Azure ML Studio

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Code and Output

```{r}
summary(cars)
```

## Slide with Plot

```{r, echo=FALSE}
plot(cars)
```

# SQL Server Machine Learnign services

# Microsoft R Server
